Abstract

### 2025-05-28 output/Letter_to_editor_reviewers.Rmd
Add data availability statement
Obfuscate at the same time all repository URLs

Notwithstanding, we have written extensive code in R for computing these parameters, which we intend to open up for public use and scrutiny in a GitHub repository that includes all the code, data, and examples (including all the R packages to re-create the necessary environment to grant computational reproducibility), allowing to generate all the tables, plots, and even the submitted versions of the manuscript.
Using dedicated functions in our code, any interested researcher will be able to compute the multidimensional parameters from the output of any MIRT software [e.g., {mirt}, @chalmers_mirt_2012; flexMIRT, @cai_flexmirt_2024].
As the journal guidelines [require a specific format for the Supplementary Material](https://www.cambridge.org/core/services/authors/publishing-supplementary-material),
we chose not to include the repository as additional material.
However, we have checked and the journal accepts and also encourages publishing additional materiales in [a proper, trusted repository](https://www.cambridge.org/core/services/where-to-share-your-data). 
We have thus made public [our GitHub repository for the manuscript](https://github.com/DaniMori/mirt-parameters) and [indexed it in Software Heritage](https://archive.softwareheritage.org/swh:1:dir:3914435e67a2b34847e36a712a181d7d9d76f35e;origin=https://github.com/DaniMori/mirt-parameters;visit=swh:1:snp:9069b256471ea08d5748e8bb021b7ee876aee724;anchor=swh:1:rev:fe49f438bf940606ae7e3c86c3c55f202e6920af) for identification with a SWHID.
For the sake of transparency, we have also made this addition to the manuscript, in section "Applications to Examples from the Literature", before the @reckase_multidimensional_2009 example:

> The interested reader can explore the complete code for these examples in the
indexed Software Heritage repository for this paper, specifically:
<https://archive.softwareheritage.org/swh:1:cnt:b104aa768ded8fc19e2cafe8cdc9e64724c4fa47;origin=https://github.com/DaniMori/mirt-parameters;visit=swh:1:snp:9069b256471ea08d5748e8bb021b7ee876aee724;anchor=swh:1:rev:fe49f438bf940606ae7e3c86c3c55f202e6920af;path=/src/Empirical_example.R>

>>>>

Notwithstanding, we have written extensive code in R for computing these parameters, which we intend to open up for public use and scrutiny in a GitHub repository that includes all the code, data, and examples (including all the R packages to re-create the necessary environment to grant computational reproducibility), allowing to generate all the tables, plots, and even the submitted versions of the manuscript.
Using dedicated functions in our code, any interested researcher will be able to compute the multidimensional parameters from the output of any MIRT software [e.g., {mirt}, @chalmers_mirt_2012; flexMIRT, @cai_flexmirt_2024].
As the journal guidelines [require a specific format for the Supplementary Material](https://www.cambridge.org/core/services/authors/publishing-supplementary-material),
we chose not to include the repository as additional material.
However, we have checked and the journal accepts and also encourages publishing additional materiales in [a proper, trusted repository](https://www.cambridge.org/core/services/where-to-share-your-data). 
We have thus made public our GitHub repository for the manuscript [Link URL obfuscated for blind peer-review] and indexed it in Software Heritage [Link URL obfuscated for blind peer-review] for identification with a SWHID.
For the sake of transparency, we have also made this addition to the manuscript, in section "Applications to Examples from the Literature", before the @reckase_multidimensional_2009 example:

> The interested reader can explore the complete code for these examples in the
indexed Software Heritage repository for this paper, specifically:
[URL obfuscated for blind peer-review]

### 2025-05-28 output/Main_text.Rmd
Add data availability statement
Obfuscate at the same time all repository URLs

The two examples are represented in Tables
\@ref(tab:empirical-table-Reckase2009-out)
and \@ref(tab:empirical-table-Tezza2018-out), respectively.
Each of these tables shows the original `r MODEL_ACRONYM` parameters
[the estimation errors in @tezza_modelo_2018 are omitted for clarity],
along with the agnostic version of the multidimensional parameters;
the $`r MDISC_AG_PARAM`$ and the $`r DISTANCE_AG_PARAM`$
are coincident with their respective original sources
[see Table 6.1 in @reckase_multidimensional_2009, p. 153; and
Table 5 in @tezza_modelo_2018, p. 926].
In the first case, the direction angles are also coincident with the values
provided in the original [@tezza_modelo_2018, do not provide these results].
In order to facilitate the comparison,
the covariance-based version of each parameter is provided in
the column next to its corresponding agnostic version.
The interested reader can explore the complete code for these examples in the
indexed Software Heritage repository for this paper, specifically:
<https://archive.softwareheritage.org/swh:1:cnt:b104aa768ded8fc19e2cafe8cdc9e64724c4fa47;origin=https://github.com/DaniMori/mirt-parameters;visit=swh:1:snp:9069b256471ea08d5748e8bb021b7ee876aee724;anchor=swh:1:rev:fe49f438bf940606ae7e3c86c3c55f202e6920af;path=/src/Empirical_example.R>

>>>>

The two examples are represented in Tables
\@ref(tab:empirical-table-Reckase2009-out)
and \@ref(tab:empirical-table-Tezza2018-out), respectively.
Each of these tables shows the original `r MODEL_ACRONYM` parameters
[the estimation errors in @tezza_modelo_2018 are omitted for clarity],
along with the agnostic version of the multidimensional parameters;
the $`r MDISC_AG_PARAM`$ and the $`r DISTANCE_AG_PARAM`$
are coincident with their respective original sources
[see Table 6.1 in @reckase_multidimensional_2009, p. 153; and
Table 5 in @tezza_modelo_2018, p. 926].
In the first case, the direction angles are also coincident with the values
provided in the original [@tezza_modelo_2018, do not provide these results].
In order to facilitate the comparison,
the covariance-based version of each parameter is provided in
the column next to its corresponding agnostic version.
The interested reader can explore the complete code for these examples in the
indexed Software Heritage repository for this paper, specifically:
[URL obfuscated for blind peer-review]
